Using R to help plan the <br> future of transport

### 2018-11-20 ms-meetup-nov18.Rmd
:rocket:

```{r osmdata-sp, eval = FALSE}
library (osmdata)
opq ("48155 de") %>%
    add_osm_feature (key = "highway") %>%
    osmdata_sp ()
```

- `osmdata_sf` `r icon::fa_long_arrow_alt_right()` .bold[Simple Features]
- `osmdata_sp` `r icon::fa_long_arrow_alt_right()` .bold[R Spatial]

```{r osmdata-sc, eval = FALSE}
library (osmdata)
opq ("48155 de") %>%
    add_osm_feature (key = "highway") %>%
    osmdata_sc ()
```

- `osmdata_sf` `r icon::fa_long_arrow_alt_right()` .bold[Simple Features]
- `osmdata_sp` `r icon::fa_long_arrow_alt_right()` .bold[R Spatial]
- `osmdata_sc` `r icon::fa_long_arrow_alt_right()` .bold[Silicate (Simplicial Complex)]

```{r osmdata-xml, eval = FALSE}
library (osmdata)
opq ("48155 de") %>%
    add_osm_feature (key = "highway") %>%
    osmdata_xml (file = "ms48155.osm")
```

- `osmdata_sf` `r icon::fa_long_arrow_alt_right()` .bold[Simple Features]
- `osmdata_sp` `r icon::fa_long_arrow_alt_right()` .bold[R Spatial]
- `osmdata_sc` `r icon::fa_long_arrow_alt_right()` .bold[Silicate (Simplicial Complex)]
- `osmdata_xml` `r icon::fa_long_arrow_alt_right()` .bold[XML / OSM]

```{r osmdata-pbf, eval = FALSE}
library (osmdata)
opq ("48155 de") %>%
    add_osm_feature (key = "highway") %>%
    osmdata_pbf (file = "ms48155.pbf")
```

@@

```{r dodgr-vertices2, eval = FALSE}
v <- dodgr_vertices (net)
dim (v); head (v)
```
```{r dodgr-vertices2-fakey, eval = TRUE, echo = FALSE, message = TRUE}
dim (v); head (v, n = 5)
```
```{r vert-sample, eval = TRUE}
pts <- sample (v$id, size = 1000)
head (pts)
```

@@

>>>>

```{r osmdata-pbf, eval = FALSE}
library (osmdata)
opq ("48155 de") %>%
    add_osm_feature (key = "highway") %>%
    osmdata_sf (file = "ms48155.pbf")
```

@@

```{r dodgr-vertices2, eval = FALSE}
v <- dodgr_vertices (net)
dim (v); head (v)
```
```{r dodgr-vertices2-fakey, eval = TRUE, echo = FALSE, message = TRUE}
v <- dodgr_vertices (net)
dim (v); head (v, n = 5)
```
```{r vert-sample, eval = TRUE}
pts <- sample (v$id, size = 1000)
head (pts)
```

@@

.fontBIG[
And can be incorporated!
]
